Nabi - A Preventative Solution Against JavaScript and Scriptless Tabnabbing Attacks

### 2015-04-28 paper/paper.tex
Finished TabShots section

\subsection{TabSol}
\begin{comment}
Another defence against tabnabbing, TabSol created by Amandeep Singh and Somanath Tripathy \cite{TabSol}, compares the hash values of the web page to detect changes and notifies the user. 
\end{comment}

>>>>

According to the testings of the creators, TabShots is said to provide large compatibility with most major sites on the internet at a seemingly acceptable processing speed.  The extensions was used on the top 1000 websites listed on Alexa.com, and the results showed that 78\% of these sites fall within the safe threshold of 5\% or less in changed blocks, meaning no compatability issues exist with that page.  About 19\% of these sites have moderate changes less than 40\%, which is the threshold for high amounts of changes, and 3\% report more than 40\% differences in changed blocks.  While the last two numbers may seem high in terms of false positives, the authors note that TabShots never interferes with the functionality of a page, and does provide a whitelist to providing overlays for these sites.  In terms of speed, testing showed that TabShots was able to prepare and calculate the image comparisions on a $1366 \times 768$ window within an average time of 284ms, which should provide little impact on browser operating time.

There are some problems with this application.  First, the performance testing of TabShots was done on a $1366 \times 768$ window.  Many users today have monitors with much larger resolutions such as $1920 \times 1080$ or $2560 \times 1440$, which provide two or four times as many pixels.  This means that TabShots will run considerably longer on these types of monitors and provided a much larger performance strain.  TabShots is designed to calculate the comparisons every time the user changes tab, which lead to very frequent occurrences of calculations depending on user behavior, and can further exaggerate TabShot's slower performance on higher resolution monitors.  Finally, the visual comparison property of TabShots leads to many occurrences of false positives that lead to the high numbers mentioned above.  Examples of non-malicious behavior that would trigger overlay occurrences would be videos, GIFs, image slideshows, overlays, and other dynamic advertisements.  The authors note that slowly images and files would flag large amounts of tile changes.  In addition, if an element was added or removed from the page, every other element on the page would shift, which would flag a major change in the picture comparison algorithm.  The uncertain performance of TabShots on large monitors or frequently changing tabs, as well as its high opportunities for false positives make TabShots a potentially unideal solution to tabnabbing. 
\subsection{TabSol}
\begin{comment}
Another defense against tabnabbing, TabSol created by Amandeep Singh and Somanath Tripathy \cite{TabSol}, compares the hash values of the web page to detect changes and notifies the user. 
\end{comment}
